Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm

### 2023-09-15 paper/SST/1-main.tex
重构：重命名
重构：使用latexdiff

%%%%%% Bibliography %%%%%%
% Replace "sample" in the \addbibresource line below with the name of your .bib file.
% \usepackage[style=nejm, 
% citestyle=numeric-comp,
% sorting=none]{biblatex}
% \addbibresource{main.bib}

@@

\begin{thebibliography}{99}

\bibitem{desiqueiraControlStrategySmooth2021}
Luanna Maria~Silva {de Siqueira} and Wei Peng.
\newblock Control strategy to smooth wind power output using battery energy
  storage system: {{A}} review.
\newblock {\em Journal of Energy Storage}, 35:102252, March 2021.

\bibitem{yangBatteryEnergyStorage2018}
Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
\newblock Battery energy storage system size determination in renewable energy
  systems: {{A}} review.
\newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
  2018.

\bibitem{choCommercialResearchBattery2015}
Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
\newblock Commercial and research battery technologies for electrical energy
  storage applications.
\newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June
  2015.

\bibitem{zhangDevelopmentProspectChinese2021}
Lihua Zhang.
\newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
  Satellite}}.
\newblock {\em Space: Science \& Technology}, 2021, January 2021.

\bibitem{schwanbeckInternationalSpaceStation2019}
Eugene Schwanbeck and Penni Dalton.
\newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
  Electric Power System}}.
\newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
  1--1. {IEEE}, September 2019.

\bibitem{yangUnbalancedDischargingAging2016}
Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
\newblock Unbalanced discharging and aging due to temperature differences among
  the cells in a lithium-ion battery pack with parallel combination.
\newblock {\em Journal of Power Sources}, 306:733--741, February 2016.

\bibitem{fengPropagationMechanismsDiagnosis2019}
Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
\newblock Propagation mechanisms and diagnosis of parameter inconsistency
  within {{Li-Ion}} battery packs.
\newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113,
  September 2019.

\bibitem{jeevarajanBatterySafetyQualifications2012}
J.~A. Jeevarajan and C.~Winchester.
\newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
\newblock {\em Interface magazine}, 21(2):51--55, January 2012.

\bibitem{pomboHybridPowerSystem2021}
Daniel~V{\'a}zquez Pombo.
\newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
\newblock {\em Space: Science \& Technology}, 2021, January 2021.

\bibitem{hanNextGenerationBatteryManagement2020a}
Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
\newblock Next-{{Generation Battery Management Systems}}: {{Dynamic
  Reconfiguration}}.
\newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December
  2020.

\bibitem{visairoReconfigurableBatteryPack2008}
H.~Visairo and P.~Kumar.
\newblock A reconfigurable battery pack for improving power conversion
  efficiency in portable devices.
\newblock In {\em 2008 7th {{International Caribbean Conference}} on
  {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.

\bibitem{heExploringAdaptiveReconfiguration2013}
Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
\newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
  Efficiency}} in {{Large-Scale Battery Systems}}.
\newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
  118--127, December 2013.

\bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
\newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}}
  an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin
  Model}}.
\newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469,
  May 2011.

\bibitem{mousavig.VariousBatteryModels2014}
S.M. Mousavi~G. and M.~Nikdel.
\newblock Various battery models for various simulation studies and
  applications.
\newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
  2014.

\bibitem{lawsonSoftwareConfigurableBattery2012}
Barrie Lawson.
\newblock A {{Software Configurable Battery}}.
\newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
  Vehicle Symposium}, 2012.

\bibitem{ciNovelDesignAdaptive2007}
Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
\newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
  for {{Power-Aware Embedded Networked Sensing Systems}}.
\newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
  Conference}}}, pages 1043--1047, November 2007.

\bibitem{alahmadBatterySwitchArray2008}
Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
\newblock Battery switch array system with application for {{JPL}}'s
  rechargeable micro-scale batteries.
\newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.

\bibitem{kimDependableEfficientScalable2010b}
Hahnsang Kim and Kang~G. Shin.
\newblock Dependable, efficient, scalable architecture for management of
  large-scale batteries.
\newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International
  Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187,
  {New York, NY, USA}, April 2010. {Association for Computing Machinery}.

\bibitem{kimBalancedReconfigurationStorage2011a}
Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo
  Poncino, and Massoud Pedram.
\newblock Balanced reconfiguration of storage banks in a hybrid electrical
  energy storage system.
\newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on
  {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.

\bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
Taesic Kim, Wei Qiao, and Liyan Qu.
\newblock A series-connected self-reconfigurable multicell battery capable of
  safe and effective charging/discharging and balancing operations.
\newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
  Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.

\bibitem{6843711}
Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
\newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
  battery systems.
\newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
  {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.

\end{thebibliography}

>>>>

%%%%%% Bibliography %%%%%%
% Replace "sample" in the \addbibresource line below with the name of your .bib file.
\usepackage[style=nejm, 
citestyle=numeric-comp,
sorting=none]{biblatex}
\addbibresource{ref.bib}

@@

% \begin{thebibliography}{99}
% 
% \bibitem{desiqueiraControlStrategySmooth2021}
% Luanna Maria~Silva {de Siqueira} and Wei Peng.
% \newblock Control strategy to smooth wind power output using battery energy
%   storage system: {{A}} review.
% \newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
% 
% \bibitem{yangBatteryEnergyStorage2018}
% Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
% \newblock Battery energy storage system size determination in renewable energy
%   systems: {{A}} review.
% \newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
%   2018.
% 
% \bibitem{choCommercialResearchBattery2015}
% Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
% \newblock Commercial and research battery technologies for electrical energy
%   storage applications.
% \newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June
%   2015.
% 
% \bibitem{zhangDevelopmentProspectChinese2021}
% Lihua Zhang.
% \newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
%   Satellite}}.
% \newblock {\em Space: Science \& Technology}, 2021, January 2021.
% 
% \bibitem{schwanbeckInternationalSpaceStation2019}
% Eugene Schwanbeck and Penni Dalton.
% \newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
%   Electric Power System}}.
% \newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
%   1--1. {IEEE}, September 2019.
% 
% \bibitem{yangUnbalancedDischargingAging2016}
% Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
% \newblock Unbalanced discharging and aging due to temperature differences among
%   the cells in a lithium-ion battery pack with parallel combination.
% \newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
% 
% \bibitem{fengPropagationMechanismsDiagnosis2019}
% Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
% \newblock Propagation mechanisms and diagnosis of parameter inconsistency
%   within {{Li-Ion}} battery packs.
% \newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113,
%   September 2019.
% 
% \bibitem{jeevarajanBatterySafetyQualifications2012}
% J.~A. Jeevarajan and C.~Winchester.
% \newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
% \newblock {\em Interface magazine}, 21(2):51--55, January 2012.
% 
% \bibitem{pomboHybridPowerSystem2021}
% Daniel~V{\'a}zquez Pombo.
% \newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
% \newblock {\em Space: Science \& Technology}, 2021, January 2021.
% 
% \bibitem{hanNextGenerationBatteryManagement2020a}
% Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
% \newblock Next-{{Generation Battery Management Systems}}: {{Dynamic
%   Reconfiguration}}.
% \newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December
%   2020.
% 
% \bibitem{visairoReconfigurableBatteryPack2008}
% H.~Visairo and P.~Kumar.
% \newblock A reconfigurable battery pack for improving power conversion
%   efficiency in portable devices.
% \newblock In {\em 2008 7th {{International Caribbean Conference}} on
%   {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
% 
% \bibitem{heExploringAdaptiveReconfiguration2013}
% Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
% \newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
%   Efficiency}} in {{Large-Scale Battery Systems}}.
% \newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
%   118--127, December 2013.
% 
% \bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
% Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
% \newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}}
%   an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin
%   Model}}.
% \newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469,
%   May 2011.
% 
% \bibitem{mousavig.VariousBatteryModels2014}
% S.M. Mousavi~G. and M.~Nikdel.
% \newblock Various battery models for various simulation studies and
%   applications.
% \newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
%   2014.
% 
% \bibitem{lawsonSoftwareConfigurableBattery2012}
% Barrie Lawson.
% \newblock A {{Software Configurable Battery}}.
% \newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
%   Vehicle Symposium}, 2012.
% 
% \bibitem{ciNovelDesignAdaptive2007}
% Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
% \newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
%   for {{Power-Aware Embedded Networked Sensing Systems}}.
% \newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
%   Conference}}}, pages 1043--1047, November 2007.
% 
% \bibitem{alahmadBatterySwitchArray2008}
% Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
% \newblock Battery switch array system with application for {{JPL}}'s
%   rechargeable micro-scale batteries.
% \newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
% 
% \bibitem{kimDependableEfficientScalable2010b}
% Hahnsang Kim and Kang~G. Shin.
% \newblock Dependable, efficient, scalable architecture for management of
%   large-scale batteries.
% \newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International
%   Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187,
%   {New York, NY, USA}, April 2010. {Association for Computing Machinery}.
% 
% \bibitem{kimBalancedReconfigurationStorage2011a}
% Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo
%   Poncino, and Massoud Pedram.
% \newblock Balanced reconfiguration of storage banks in a hybrid electrical
%   energy storage system.
% \newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on
%   {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.
% 
% \bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
% Taesic Kim, Wei Qiao, and Liyan Qu.
% \newblock A series-connected self-reconfigurable multicell battery capable of
%   safe and effective charging/discharging and balancing operations.
% \newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
%   Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
% 
% \bibitem{6843711}
% Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
% \newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
%   battery systems.
% \newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
%   {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
% 
% \end{thebibliography}
